Constraining gravitational wave amplitude birefringence with GWTC-3

### 2023-02-28 src/tex/ms.tex
minor text change

% Violin plot
Figure \ref{fig:violin_kappa} shows the main result of our GWTC-3 analysis.
as represented by the posterior distribution on $\kappa$ (abscissa) obtained for each event (ordinate), colored by the distance of the respective posterior mean from the origin in units of standard deviation, i.e., $|\mu/\sigma|$.
The collective measurement obtained by assuming a shared $\kappa$ across events, Eq.~\eqref{eq:restricted_posterior}, is represented by its 90\%-credible symmetric interval (blue band) around the median (blue line);
this joint measurement is fully consistent with $\kappa = 0$ (dashed line), meaning we find no evidence for birefringence.

@@

The event that shows the largest tension with $\kappa = 0$ is GW170818, for which $|\mu / \sigma| =$ \variable{output/GW170818_constraint.txt}.
\mi{THOMAS: we don't need that many significant figures, $2.0$ would do}
Additionally, the GW200129 result shows features that could be indicative of contamination from non-Gaussian instrumental noise.
We discuss both of these events in detail below.

>>>>

% Violin plot
Figure \ref{fig:violin_kappa} shows the main result of our GWTC-3 analysis.
As represented by the posterior distribution on $\kappa$ (abscissa) obtained for each event (ordinate), colored by the distance of the respective posterior mean from the origin in units of standard deviation, i.e., $|\mu/\sigma|$.
The collective measurement obtained by assuming a shared $\kappa$ across events, Eq.~\eqref{eq:restricted_posterior}, is represented by its 90\%-credible symmetric interval (blue band) around the median (blue line);
this joint measurement is fully consistent with $\kappa = 0$ (dashed line), meaning we find no evidence for birefringence.

@@

The event that shows the largest tension with $\kappa = 0$ is GW170818, for which $|\mu / \sigma| =$ \variable{output/GW170818_constraint.txt}.
Additionally, the GW200129 result shows features that could be indicative of contamination from non-Gaussian instrumental noise.
We discuss both of these events in detail below.
